\begin{publications}
\begin{enumerate}[]
	\item \textbf{期刊文章}
	\begin{enumerate}[1.]
		\item \textbf{Q. Huang}, Y. Wu, K. Ma, J. Zhang, W. Xie, X. Fu, Y. Shi, K. Chen, J. He, D. Van Thourhout, G. Roelkens, L. Liu, and S. He. Low driving voltage band-filling based III-V-on-silicon electroabsorption modulator. Appl. Phys. Lett., 108: 141104, 2016.
		\item \textbf{Q. Huang}, K. Ma, and S. He. Experimental Demonstration of Single Mode-Splitting in Microring With Bragg Gratings. IEEE Photonics Thechnology Letters, 27(13): 1402-1405, 2015.
		\item \textbf{Q. Huang}, J. Chen, L. Liu, Y. Tang, and S. He. Ultracompact tapered coupler for the Si/III-V heterogeneous integration. Applied Optics, 54(14): 4327-4332, 2015.
		\item \textbf{Q. Huang}, F. Bao, and S. He. Nonlocal effects in a hybrid plasmonic waveguide for nanoscale confinement. Optics Express, 21(2): 1430-1439, 2013.
		\item K. Chen, \textbf{Q. Huang (并列一作)}, J. Zhang, J. Chen, X. Fu, C. Zhang, K. Ma, Y. Shi, D. Van Thourhout, G. Roelkens, L. Liu, and S. He. Wavelength-multiplexed duplex transceiver based on IIIV/Si hybrid integration for off-chip 
		and on-chip optical interconnects. IEEE Photonics Journal, 8(1): 1-10, 2016. 		
		\item A. Li, \textbf{Q. Huang}, and W. Bogaerts. Design of a single all-silicon ring resonator with a 150 nm free spectral range and a 100 nm tuning range around 1550 nm. Photonics Research, 4(2): 84-92, 2016.
		\item P. Xu, \textbf{Q. Huang}, and Y. Shi. Silicon hybrid plasmonic Bragg grating reflectors and high Q-factor micro-cavities. Optics Communications, 289(15): 81-84, 2013.		
		\item X. Fu, J. Cheng, \textbf{Q. Huang}, Y. Hu, W. Xie, M. Tassaert, J. Verbist, K. Ma, J. Zhang, K. Chen, et al. 5 x 20 Gb/s heterogeneously integrated III-V on silicon electro-absorption modulator array with arrayed waveguide grating multiplexer. Optics Express, 23(14): 18686-18693, 2015.
		\item X. Wang, X. Guan,\textbf{ Q. Huang}, J. Zheng, Y. Shi, and D. Dai. Suspended ultra-small disk resonator on silicon for optical sensing. Optics Letters, 38(24): 5405-5408, 2013.
		\item J. Cheng, Y. Zhu, C. Zhao,\textbf{ Q. Huang}, and L. Liu. Double-side processed III-V nanowire waveguide on a silicon substrate. Optical and Quantum Electronics, 47(10): 3381-3390, 2015.
		\item G. Roelkens, A. Abassi, P. Cardile, U. Dave, A. de Groote, Y. de Koninck, S. Dhoore, X. Fu, A. Gassenq, N. Hattasan, \textbf{Q. Huang}, S. Kumari, S. Keyvaninia, B. Kuyken, L. Li, P. Mechet, M. Muneeb, D. Sanchez, H. Shao, T. Spuesens, A. Z. Subramanian, S. Uvin, M. Tassaert, K. van Gasse, J. Verbist, R. Wang, Z. Wang, J. Zhang, J. van Campenhout, X. Yin, J. Bauwelinck, G. Morthier, R. Baets, and D. Van Thourhout. III-V-on-Silicon Photonic Devices for Optical Communication and Sensing. Photonics, 2(3): 969-1004, 2015.
	\end{enumerate}
	\item \textbf{会议文章}
	\begin{enumerate}[1.]
		\item \textbf{Q. Huang}, K. Ma, and S. He. FSR-Free Filter Based on a Coupled Microring Grating System. Optical Fiber Communication Conference, Tu3A. 1, 2015 
		\item \textbf{Q. Huang}, J. Cheng, L. Liu, Y. Tang, S. He. Ultracompact adiabatic tapered coupler for the Si/III-V heterogeneous integration. PIERS Proceedings, 920-924, 2014.
		\item \textbf{Q. Huang}, F. Bao, Y. Shi, D. Dao, and S. He. Novel silicon hybrid plasmonic waveguide with an inverted metal nano-rib for a nanoscale light confinement. Asia Communications and Photonics Conference, AS2H-3, 2012.
		\item S. Huang, \textbf{Q. Huang}, K. Ma, J. Zhang, Y. Shi, D. Dai, T. Lu, and S. He. Design, optimization and fabrication of two-dimension high contrast subwavelength grating (HCG) mirror on Silicon-on-insulator. Next-Generation Electronics (ISNE), International Symposium on Taipei, 1-3, 2015.
		\item X. Fu, \textbf{Q. Huang}, Y. Hu, M. Tassaert, J. Verbist, J. Cheng, K. Ma, J. Zhang, K. Chen, C. Zhang, Y. Shi, J. Bauwelinck, G. Roelkens, and S. He. 5 x 20 Gb/s III-V on Silicon Electroabsorption Modulator Array Heterogeneously Integrated with a 1.6nm Channel-Spacing Silicon AWG. in CLEO: 2015, STu4F.2, 2015.		
		\item K. Chen, Y. Zhu, J. Cheng, \textbf{Q. Huang}, X. Fu, J. Zhang, J. Liu, G. Roelkens, and L. Liu. IIIV/Si hybrid integrated devices for optical interconnect. Proc. SPIE 9366, Smart Photonic and Optoelectronic Integrated Circuits XVII, 93660I, 2015.
	\end{enumerate}
\end{enumerate}
\end{publications}
